Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-07-20 apj.tex
a study plot and removal of comment

The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
deviations of the magnitude residuals $\sigma_X$
\color{red}
in the $U$ and $B$ bands.  The   $<1\sigma$ changes in $\pmb{\gamma}$ lead to a slight increase in the 
 \citetalias{1999PASP..111...63F}
$R^F$-parameter 68\% credible interval
from $2.26$--$2.63$ to $2.31$--$2.69$.
\color{black}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameters& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0039^{+0.0009}_{-0.0009}$
&
$0.0013^{+0.0008}_{-0.0007}$
&
$0.0013^{+0.0006}_{-0.0006}$
&
$0.0013^{+0.0005}_{-0.0005}$
&
$0.0025^{+0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   2.1^{+   1.4}_{  -0.6}$
&
$   0.0^{+   0.1}_{  -0.2}$
&
$  \dots $
&
$   0.0^{+   0.2}_{  -0.1}$
&
$   1.0^{+   1.1}_{  -0.5}$
\\
$\beta_X$
&
$ 0.032^{+ 0.003}_{-0.003}$
&
$ 0.025^{+ 0.002}_{-0.002}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.021^{+ 0.002}_{-0.002}$
&
$ 0.020^{+ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.24^{+  0.05}_{ -0.05}$
&
$ -0.02^{+  0.03}_{ -0.03}$
&
$   \dots$
&
$ -0.19^{+  0.01}_{ -0.01}$
&
$ -0.23^{+  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{+0.0011}_{-0.0011}$
&
$-0.0000^{+0.0009}_{-0.0009}$
&
$0.0005^{+0.0008}_{-0.0008}$
&
$0.0005^{+0.0007}_{-0.0007}$
&
$-0.0002^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.41^{+  2.27}_{ -1.94}$
&
$ -0.37^{+  1.59}_{ -1.26}$
&
$   \dots$
&
$ -0.10^{+  0.30}_{ -0.29}$
&
$ -0.80^{+  1.54}_{ -1.29}$
\\
$\gamma^0_X$
&
$ 61.66^{+  3.97}_{ -3.86}$
&
$ 50.09^{+  3.25}_{ -3.16}$
&
$ 37.41^{+  2.69}_{ -2.60}$
&
$ 28.81^{+  2.35}_{ -2.31}$
&
$ 20.76^{+  2.17}_{ -2.12}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.65^{+  0.06}_{ -0.05}$
&
$  0.34^{+  0.03}_{ -0.03}$
&
$   \dots$
&
$ -0.23^{+  0.01}_{ -0.01}$
&
$ -0.45^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.47^{+  3.70}_{ -4.37}$
&
$-11.09^{+  3.02}_{ -3.57}$
&
$-13.59^{+  2.47}_{ -2.81}$
&
$-12.82^{+  2.14}_{ -2.40}$
&
$-11.66^{+  2.25}_{ -2.32}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.30^{+  0.19}_{ -0.21}$
&
$ -0.18^{+  0.11}_{ -0.12}$
&
$   \dots$
&
$ -0.06^{+  0.06}_{ -0.06}$
&
$ -0.15^{+  0.12}_{ -0.12}$
\\
${{\delta_X/\delta_U-1}}$
&
$   \dots$
&
$ -0.22^{+  0.35}_{ -0.32}$
&
$ -0.73^{+  0.51}_{ -0.61}$
&
$ -0.91^{+  0.43}_{ -0.69}$
&
$ -1.17^{+  0.46}_{ -0.93}$
\\
$\sigma_X$
&
$ 0.053^{+ 0.009}_{-0.011}$
&
$ 0.018^{+ 0.012}_{-0.012}$
&
$ 0.020^{+ 0.004}_{-0.005}$
&
$ 0.010^{+ 0.008}_{-0.007}$
&
$ 0.040^{+ 0.006}_{-0.005}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the global fit Parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
\end{table}

@@

The posteriors of the $\pmb{\delta}$ parameters are shown  in
Figure~\ref{deltacorner:fig}.
In the full 5-dimensional space,
the point $\delta_X=0$  lies on the 85\%-ile contour.
Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ that results in the bimodal peaks in the distribution.
To aid in the visualization of the results,
we break this degeneracy by imposing  that the $D$ of the one supernova with the highest signal-to-noise be positive.
The resulting posterior contours of $\pmb{\delta}$ with this additional
condition are shown in Figure~\ref{deltacorner:fig}.
The modes of $\pmb{\delta}$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in $UBVRI$ respectively.
The values of $\delta_X/\delta_U-1$, statistics insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output25/delta_corner.pdf}
     \includegraphics[width=2.8in]{output25/delta_corner_flipped.pdf}
   \caption{Left:  Posterior contours for $\pmb{\delta}$ for Model~II.
   Right: The same posteriors after imposing that  the one supernova with  the $D$ of the one supernova with the highest signal-to-noise be positive.
     Lines for $\pmb{\delta}=0$ are overplotted.
   \label{deltacorner:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output25/deltaratio.pdf}
   \caption{Median values of $\delta_X/\delta_U$ in the 5 bands and corresponding 68\% intervals for for Model~II.
   A dotted line at zero is shown for reference.
   \label{deltaratio:fig}}
\end{figure}

@@

The distributions of both sources of color excess $E(B-V)$ and
 $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
 (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
The standard deviations of  the median $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
%-----
0.075
and 0.014
%-----
mag respectively.
The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
component.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output25/ebv.pdf}
   \includegraphics[width=2.8in]{output25/ebv_delta.pdf}
      \caption{Left: Ideograms of the external $E(B-V)$ and
   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
   Right: Ideogram and histogram of the medians of $E_\delta(B-V)$ on an enlarged scale.
   \label{ebv:fig}}
\end{figure}

@@

The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are
\color{purple}
not statistically significant.
\color{black}
This has two important implications:
First, while the degeneracies in the model could allow a single physical color effect to be
distributed between both intrinsic and extrinsic parameters, from the correlations
there is no evidence
that this occurs.
Second, the intrinsic term cannot be attributed to non-linearity that is inherent to the broad-band extinction in dust models, since
in that case a correlation between the  $k$'s and $D$ would be expected.

@@

\color{red}
The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$ for better signal-to-noise) can be expressed as
\color{black}
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} \\
\frac{\delta_X}{\delta_U} \\
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.88 & 1.16 \\
-5.00 & 0.73 \\
0.24 & 0.46
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_{\gamma^0} \\
\vec{\epsilon}_{\gamma^1} \\
\vec{\epsilon}_{\delta}
\end{pmatrix},
\label{model2trans:eqn}
\end{equation}
where the residual vectors are 
\begin{align}
\begin{split}
\vec{\epsilon}_{\gamma^0} &=\{0.07, -0.07, -0.07,  0.06,  0.02\},\\
\vec{\epsilon}_{\gamma^1} &=\{ -0.04, 0.14,  -0.24,  0.32, -0.22\},\\
\vec{\epsilon}_{\delta} &=\{ -0.05, 0.08,  -0.03,  -0.09, -0.12\}
\end{split}
\label{model2res:eqn}
\end{align}
The $\pmb{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
$\vec{\epsilon}_{\gamma^1} $
quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
These results are similar to those of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.
\color{red}
The $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
\color{black}

\color{red}
The significance of the results is evaluated using simulated datasets.
For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values found in
\S\ref{model:sec} and the same noise as our data.  The input values of $\pmb{\delta}$ are set to zero.
In Figure~\ref{pvalues_delta2:fig}, the squared amplitudes  $\pmb{\delta}^2$
from the null realizations are compared with that of our fit to the data.  Depending on the choice either the  $-1$, 0, or $1$-sigma
value, the data value is at the 90--98\%-ile.  Contrast these $p$-values with the 85\%-ile contour on which $\pmb{\delta}=0$ lies
in the Bayesian posterior.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.9in]{output25_sim_null/pvalues_delta2.pdf} 
  \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
            \caption{ The squared length $\pmb{\delta}^2$ (left) and relative length perpendicular to the plane defined by $\pmb{\gamma}$ $\delta_\perp^2/\delta^2$ for 50 independent simulated data sets with input $\delta=0$.  The fits
            are ordered by the median value, the null realizations are shown in blue and the result from our data is shown in red.
            \label{pvalues_delta2:fig}}
\end{figure}

The significance of the close projection of $\pmb{\delta}$ onto the plane defined by the $\pmb{\gamma}$'s is shown
in  Figure~\ref{pvalues_delta2:fig}, which plots the relative amplitude projected out of the plane $\delta_\perp^2/\delta^2$ for the null realizations
and our data.  Our data has smaller value than all the realizations for $-1$, 0, or $1$-sigma values.  This alleviates
the concern that our model and sampling spuriously produce $\pmb{\delta}$ closely aligned with the $\pmb{\gamma}$--plane, i.e.\
the small  $\delta_\perp^2/\delta^2$ of our data is not expected to be due to noise at 98\%.

The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
biases in the best fit value.  The stack of   $\pmb{\delta}$ is shown in Figure~\ref{simnulldelta:fig}.  The correlations between the parameters
and the bimodality of each posterior results in biases in the stack, with
modes at $\mp 0.67$, $\pm0.14$, $\pm0.13$,  $\mp0.03$, $\mp0.52$.
The input length of $\pmb{\delta}$ is zero, therefore any statistical
fluctuation biases the value high.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
            \caption{Stacked $\pmb{\delta}$ posterior contours for 20 independent simulated data sets with input $\pmb{\delta}=0$.
            \label{simnulldelta:fig}}
\end{figure}
We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
relative to the statistical uncertainties. 
Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
with the extracted distributions.  Also, 
there is a tendency for the slope parameters associated with the spectral features to be slightly underestimated, which is an expected consequence of 
the uncertainties in the predictor variable that lead to 
regression dilution \citep{spearman04}. 
\color{black}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $U$ band of ten independent simulated data sets.  Lines show the values of the input values.
            \label{simglobal1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $B$ band of ten independent simulated data sets.   Lines show the values of the input values.
 \label{simglobal2:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $V$ band of ten independent simulated data sets.   Lines show the values of the input values.
 \label{simglobal3:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $R$ band of ten independent simulated data sets.   Lines show the values of the input values.
\label{simglobal4:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
         \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $I$ band of ten independent simulated data sets.   Lines show the values of the input values.
 \label{simglobal5:fig}}
\end{figure}

@@

\color{black}
\subsection{Physical Motivation}

Our third supernova parameter does not have a monotonic influence on supernova magnitudes as a function
of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes
for this component.  Absorption and re-emission of light
over broad bands are the most obvious candidate for producing this behavior.

\color{red}
Speculate on third parameter.
\color{black}

Although the $D$ parameter has been referred to as ``intrinsic'', due to its placement in the model and the correspondence
of the $k$ parameters with those of extrinsic two-parameter dust models, the analysis cannot quantitatively distinguish
whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.

We stress that our $\pmb{\delta}$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
the contribution perpendicular to the $\pmb{\gamma}$ vectors.

>>>>

The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
deviations of the magnitude residuals $\sigma_X$
\color{red}
in the $U$ and $B$ bands.
\color{black}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameters& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0039^{+0.0009}_{-0.0009}$
&
$0.0013^{+0.0008}_{-0.0007}$
&
$0.0013^{+0.0006}_{-0.0006}$
&
$0.0013^{+0.0005}_{-0.0005}$
&
$0.0025^{+0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   2.1^{+   1.4}_{  -0.6}$
&
$   0.0^{+   0.1}_{  -0.2}$
&
$  \dots $
&
$   0.0^{+   0.2}_{  -0.1}$
&
$   1.0^{+   1.1}_{  -0.5}$
\\
$\beta_X$
&
$ 0.032^{+ 0.003}_{-0.003}$
&
$ 0.025^{+ 0.002}_{-0.002}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.021^{+ 0.002}_{-0.002}$
&
$ 0.020^{+ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.24^{+  0.05}_{ -0.05}$
&
$ -0.02^{+  0.03}_{ -0.03}$
&
$   \dots$
&
$ -0.19^{+  0.01}_{ -0.01}$
&
$ -0.23^{+  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{+0.0011}_{-0.0011}$
&
$-0.0000^{+0.0009}_{-0.0009}$
&
$0.0005^{+0.0008}_{-0.0008}$
&
$0.0005^{+0.0007}_{-0.0007}$
&
$-0.0002^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.41^{+  2.27}_{ -1.94}$
&
$ -0.37^{+  1.59}_{ -1.26}$
&
$   \dots$
&
$ -0.10^{+  0.30}_{ -0.29}$
&
$ -0.80^{+  1.54}_{ -1.29}$
\\
$\gamma^0_X$
&
$ 61.66^{+  3.97}_{ -3.86}$
&
$ 50.09^{+  3.25}_{ -3.16}$
&
$ 37.41^{+  2.69}_{ -2.60}$
&
$ 28.81^{+  2.35}_{ -2.31}$
&
$ 20.76^{+  2.17}_{ -2.12}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.65^{+  0.06}_{ -0.05}$
&
$  0.34^{+  0.03}_{ -0.03}$
&
$   \dots$
&
$ -0.23^{+  0.01}_{ -0.01}$
&
$ -0.45^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.47^{+  3.70}_{ -4.37}$
&
$-11.09^{+  3.02}_{ -3.57}$
&
$-13.59^{+  2.47}_{ -2.81}$
&
$-12.82^{+  2.14}_{ -2.40}$
&
$-11.66^{+  2.25}_{ -2.32}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.30^{+  0.19}_{ -0.21}$
&
$ -0.18^{+  0.11}_{ -0.12}$
&
$   \dots$
&
$ -0.06^{+  0.06}_{ -0.06}$
&
$ -0.15^{+  0.12}_{ -0.12}$
\\
${{\delta_X/\delta_U-1}}$
&
$   \dots$
&
$ -0.22^{+  0.35}_{ -0.32}$
&
$ -0.73^{+  0.51}_{ -0.61}$
&
$ -0.91^{+  0.43}_{ -0.69}$
&
$ -1.17^{+  0.46}_{ -0.93}$
\\
$\sigma_X$
&
$ 0.053^{+ 0.009}_{-0.011}$
&
$ 0.018^{+ 0.012}_{-0.012}$
&
$ 0.020^{+ 0.004}_{-0.005}$
&
$ 0.010^{+ 0.008}_{-0.007}$
&
$ 0.040^{+ 0.006}_{-0.005}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
\end{table}

@@

The posteriors of the $\pmb{\delta}$ parameters are shown  in
Figure~\ref{deltacorner:fig}.
In the full 5-dimensional space,
the point $\delta_X=0$, i.e.\ no effect on magnitude by a third parameter,  lies on the 85\%-ile contour.
Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ degeneracy that results in a bimodal posterior.
To aid in the visualization of the results,
we break this degeneracy by imposing  that the $D$ of the one supernova with the highest signal-to-noise be positive.
The new posterior contours of $\pmb{\delta}$ with this added
condition are shown in Figure~\ref{deltacorner:fig}.
The shapes of the new $\pmb{\delta}$ posteriors are somewhat distorted compared to the original.
Despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
resulting in changes in the shape of the $\pmb{\delta}$ posteriors when  $D$ to forced to be positive.   
The modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in for $X=UBVRI$ respectively.
The values of $\delta_X/\delta_U-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output25/delta_corner.pdf}
     \includegraphics[width=2.8in]{output25/delta_corner_flipped.pdf}
   \caption{Left:  Model~II posterior contours for $\pmb{\delta}$.
   Right: The same posteriors after imposing that $D$ of the one supernova with highest signal-to-noise be positive.
     Lines for $\pmb{\delta}=0$ are overplotted.
   \label{deltacorner:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output25/deltaratio.pdf}
   \caption{Model~II median values  and corresponding 68\% intervals for $\delta_X/\delta_U$ in the 5 bands.
   A dotted line at zero is shown for reference.
   \label{deltaratio:fig}}
\end{figure}

@@

The distributions of both sources of color excess $E(B-V)$ and
 $E_\delta(B-V) \equiv   (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
 (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
The standard deviations of  the median $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
%-----
0.075
and 0.014
%-----
mag respectively.
The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
component.   The $E_\delta(B-V)$ standard deviation is comparable to its measurement uncertainty per-supernova, showing that
the significance of $\pmb{\delta}$
is drawn from the ensemble of objects and
would be difficult to deduce from the color excess of individual supernovae.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output25/ebv.pdf}
   \includegraphics[width=2.8in]{output25/ebv_delta.pdf}
      \caption{Left: Ideograms of the external $E(B-V)$ and
   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
   Right: Ideogram and histogram of the medians of $E_\delta(B-V)$ on an enlarged scale.
   \label{ebv:fig}}
\end{figure}

@@

The correlation coefficients between the ``intrinsic''  ($A_{\delta U}$) and ``extrinsic''
($E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$)  parameters are
\color{purple}
consistent with zero.
Their independence implies that a single physical parameter is not being artificially attributed to two
model parameters.  One could have expected this to occur since our linear model does not precisely
describe broad-band magnitudes that are non-linear with respect to dust parameters. A strong
correlation between the parameters would of complicated any claims of the detection of a third independent supernova parameter.
\color{black}

@@

\color{red}
The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
in terms of the $a$ and $b$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
\color{black}
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} \\
\frac{\delta_X}{\delta_U} \\
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.88 & 1.16 \\
-5.00 & 0.73 \\
0.24 & 0.46
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_{\gamma^0} \\
\vec{\epsilon}_{\gamma^1} \\
\vec{\epsilon}_{\delta}
\end{pmatrix},
\label{model2trans:eqn}
\end{equation}
where the residual vectors
\begin{align}
\begin{split}
\vec{\epsilon}_{\gamma^0} &=\{0.07, -0.07, -0.07,  0.06,  0.02\},\\
\vec{\epsilon}_{\gamma^1} &=\{ -0.04, 0.14,  -0.24,  0.32, -0.22\},\\
\vec{\epsilon}_{\delta} &=\{ -0.05, 0.08,  -0.03,  -0.09, -0.12\}
\end{split}
\label{model2res:eqn}
\end{align}
are perpendicular to $a$ and $b$.
The $\pmb{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
$\vec{\epsilon}_{\gamma^1} $
quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
\color{red}
 $\pmb{\delta}$ too
has a significant projection onto the dust plane, as the $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
The transformation yields
a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, slightly shifted higher relative to the results of Model~I.
\color{black}

\color{red}
The significance of the results is evaluated using simulated datasets.
For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values of the 
parameter posteriors found in
\S\ref{model:sec}, and using the same noise as our data.  The input $\pmb{\delta}$-vector is set to zero.
Figure~\ref{pvalues_delta2:fig} shows results of fits of these null-realizations in comparison to the results using the real data.
The influence of the third parameter on magnitudes is measured by the squared amplitude  $\delta^2$.
Depending on the choice between the  $-1$, 0, or $1$-sigma
value of  $\delta^2$, the data value is in the largest 90--98\%-ile.  Recall that in the Bayesian posterior
$\pmb{\delta}=0$ lies on the 85\%-ile contour.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.9in]{output25_sim_null/pvalues_delta2.pdf} 
  \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\pmb{\gamma}$, $\delta_\perp^2/\delta^2$, for 50 independent simulated data sets with input $\delta=0$.  The fits
            are ordered by the median value, the null realizations are shown in blue and the result from our data is shown in red.
            \label{pvalues_delta2:fig}}
\end{figure}

Figure~\ref{pvalues_delta2:fig} also shows the 
relative projection of $\pmb{\delta}$  perpendicular to the plane defined by the $\pmb{\gamma}$'s, $\delta_\perp^2/\delta^2$,
for the 50 null realizations
and our data.  The data gives smaller value than all the realizations for $-1$, 0, or $1$-sigma values.  
Our model and analysis are unlikely to spuriously produce a $\pmb{\delta}$ as closely aligned with the $\pmb{\gamma}$--plane
as derived from our data, as its small  $\delta_\perp^2/\delta^2$  is not expected from a null signal at $>98$\%.

Parameter biases that arise as part of our analysis methodology are measured through simulation.
We realize 50 random realizations of data with input  parameters equal to the median values found in
this Section, except for $\pmb{\delta}$ which is assigned the modes presented earlier, and the same noise as our data.  The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
biases in the best fit value.
The stack of  $\pmb{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias in the
modes from the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ relative to the stacked modes $(-1.10, -0.98, -0.41, -0.09, 0.40)$
that is smaller than the statistical uncertainty of a single analysis.
The posterior stacks for the other global parameters 
are shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
relative to the statistical uncertainties. 
Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
with the extracted distributions.  Also, 
there is a tendency for the slope parameters associated with the spectral features to be slightly underestimated, which is an expected consequence of 
the uncertainties in the predictor variable that lead to 
regression dilution \citep{spearman04}.
\color{black}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
            \caption{Stacked $\pmb{\delta}$ posterior contours for 50 independent simulated data sets with input $\pmb{\delta}=0$.
            The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
            \label{simdelta:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $U$ band of ten independent simulated data sets.  The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
            \label{simglobal1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $B$ band of ten independent simulated data sets.  The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
 \label{simglobal2:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $V$ band of ten independent simulated data sets.   The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data. \label{simglobal3:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $R$ band of ten independent simulated data sets.   The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
\label{simglobal4:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
         \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $I$ band of ten independent simulated data sets.  The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
 \label{simglobal5:fig}}
\end{figure}

@@

\subsection{Physical Motivation}
